dispRity simulate data

### 2017-01-10 doc/dispRity-simulate_data.Rmd

```{r}
set.seed(1)
## tree
my_tree <- rcoal(15)
## matrix
morpho_mat <- sim.morpho(my_tree, characters = 100, model = "ER",
    rates = c(rgamma, 0.5, 1), invariant = TRUE)
check.morpho(morpho_mat, my_tree)
```

>>>>

```{r}
set.seed(1)
## tree
my_tree <- rcoal(15)
## matrix
morpho_mat <- sim.morpho(my_tree, characters = 100, model = "ER",
    rates = c(rgamma, rate = 100, shape = 5), invariant = FALSE)
check.morpho(morpho_mat, my_tree)
```
